An Open System for\\ Managing Short Programming Exercises

### 2013-08-08 paper/talk.tex
add conference name to title slide
spell Petersen correctly
revise estimate about number of users/hosting cost

\title[ICER 2013]{An Open System for\\
Managing Short Programming Exercises}
\author[Papancea et.\ al.]{Andrei Papancea\textsuperscript{*}, Jaime Spacco\textsuperscript{*}, and David Hovemeyer\textsuperscript{$\dagger$}}
\institute[Knox, YCP]{
\begin{minipage}[t]{1.1in}
\begin{center}
{{\ }\\
\textsuperscript{*}Knox College}
\vskip .1in
\includegraphics[height=.8in]{images/KnoxLogo}
\end{center}
\end{minipage}
\begin{minipage}[t]{1.1in}
\begin{center}
{\textsuperscript{$\dagger$}York College\\
of Pennsylvania}
\vskip .1in
\includegraphics[height=.8in]{images/YCPLogo}
\end{center}
\end{minipage}
}
\date[August, 2013]{August 12, 2013}

@@

\begin{itemize}
  \item Make programming exercises written by many people available
        for whatever uses are appropriate
  \begin{itemize}
    \item Our need: exercises to assign in the context of a course
    \item Related work: PCRS (Peterson et.\ al., SIGCSE 2013), in-class
          exercises to support peer instruction
    \item We can imagine lots of other uses: for example, Codecademy-style
          self-learning
  \end{itemize}
  \item Make the {\em sharing} of exercises a subject of research
  \begin{itemize}
    \item What kinds of exercises are most easily reused?
    \item How can exercises be classified and organized?
  \end{itemize}
\end{itemize}

@@

\begin{itemize}
  \item Open source (AGPL v3)
  \item Supports exercises in Java, Python, Ruby, and C/C++
  \item Collects fine-grained edit sequence of each student's work
  \item Repository of freely-redistributable (CC-BY-SA) exercises:
        \url{https://cloudcoder.org/repo}
  \item Requires two Linux servers to host (one network-facing)
    \begin{itemize}
    \item Relatively easy to install
    \item Known to support 60+ concurrent users with modest hardware
    \item Load testing experiments successful with 350+ concurrent users
          on higher-end hardware
    \item Cost to host per course-semester: perhaps \$1-\$3 per student
          (e.g., using Amazon EC2)
    \end{itemize}
\end{itemize}

@@

>>>>

\title[ICER 2013]{An Open System for\\
Managing Short Programming Exercises}
\author[Papancea et.\ al.]{Andrei Papancea\textsuperscript{*}, Jaime Spacco\textsuperscript{*}, and David Hovemeyer\textsuperscript{$\dagger$}}
\institute[Knox, YCP]{
\begin{minipage}[t]{1.1in}
\begin{center}
{{\ }\\
\textsuperscript{*}Knox College}
\vskip .1in
\includegraphics[height=.8in]{images/KnoxLogo}
\end{center}
\end{minipage}
\begin{minipage}[t]{1.1in}
\begin{center}
{\textsuperscript{$\dagger$}York College\\
of Pennsylvania}
\vskip .1in
\includegraphics[height=.8in]{images/YCPLogo}
\end{center}
\end{minipage}
}
\date[August, 2013]{ICER\\
August 12, 2013}

@@

\begin{itemize}
  \item Make programming exercises written by many people available
        for whatever uses are appropriate
  \begin{itemize}
    \item Our need: exercises to assign in the context of a course
    \item Related work: PCRS (Petersen et.\ al., SIGCSE 2013), in-class
          exercises to support peer instruction
    \item We can imagine lots of other uses: for example, Codecademy-style
          self-learning
  \end{itemize}
  \item Make the {\em sharing} of exercises a subject of research
  \begin{itemize}
    \item What kinds of exercises are most easily reused?
    \item How can exercises be classified and organized?
  \end{itemize}
\end{itemize}

@@

\begin{itemize}
  \item Open source (AGPL v3)
  \item Supports exercises in Java, Python, Ruby, and C/C++
  \item Collects fine-grained edit sequence of each student's work
  \item Repository of freely-redistributable (CC-BY-SA) exercises:
        \url{https://cloudcoder.org/repo}
  \item Requires two Linux servers to host (one network-facing)
    \begin{itemize}
    \item Relatively easy to install
    \item Known to support 60+ concurrent users with modest hardware
    \item Load testing experiments successful with 700+ concurrent users
          on moderate server hardware
      \begin{itemize}
      \item Compiling and testing submissions requires significant
            CPU resources, but is easy to scale up by adding more
            build servers
      \end{itemize}
    \item Cost to host per course-semester: perhaps \$1-\$3 per student
          (e.g., using Amazon EC2)
    \end{itemize}
\end{itemize}

@@

\begin{itemize}
\item Experiences:
\end{itemize}
